Privacy Analysis of a Mobile Sensor Application

### 2015-01-07 paper.tex
resized figures

\input{./figures/IT-Systems}

@@

%\input{./figures/LG-Implicit-Sensor-Privacy-Matrix}

@@

%\includegraphics{../diagrams/png/itsec-ref-model-grimm.png}
\input{./figures/The-IT-Security-Reference-Model-Grimm}

@@

%\includegraphics{../diagrams/png/itsec-ref-model-grimm-procedure.png}
\input{./figures/The-IT-Security-Reference-Analysis-Grimm}

@@

\input{./figures/LG-Conflicts-Of-Interests}
%TODO: Adapt Figure

@@

\input{./figures/LG-Vulnerabilities}

@@

\input{./figures/Threat-Example}

@@

% \label{figure:Threats}
\input{./figures/Threats}

>>>>

%input{./figures/IT-Systems}
\begin{figure}[h]
\centering
\includegraphics[width=0.7\textwidth]{diagrams/png/it-systems.png}

\begin{flushleft}
\scriptsize
\textbf{Legend:}
\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt

\item
\textbf{(a) Citizen:} 
User of the L+G client application whose privacy is at stake.

\item
\textbf{(b) Service Provider:} Provides technical infrastructure.

\item
\textbf{(c) Local Authority:} Provider of the L+G system.

\item
\textbf{(d) Mobile Device:}
Runs the L+G client application, produces and stores data sensitive to the users privacy.

\item
\textbf{(e) Data Center:} Runs the L+G services, processes and stores user data.

\item
\textbf{(f) Report Tool:} Interface to aggregated user data.

\end{itemize}
\end{flushleft}

\caption{IT Systems}
\label{figure:IT Systems}
\end{figure}

@@

%input{./figures/LG-Implicit-Sensor-Privacy-Matrix}

@@

%\includegraphics{../diagrams/png/itsec-ref-model-grimm.png}
%input{./figures/The-IT-Security-Reference-Model-Grimm}
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{diagrams/png/itsec-ref-model-grimm.png}
\caption{The IT Security Reference Model (Grimm)}
\label{fig:refmodel}
\end{figure}

@@

%includegraphics{../diagrams/png/itsec-ref-model-grimm-procedure.png}
%input{./figures/The-IT-Security-Reference-Analysis-Grimm}
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{diagrams/png/itsec-ref-model-grimm-procedure.png}
\caption{The IT Security Reference Analysis (Grimm)}
\end{figure}

@@

%input{./figures/LG-Conflicts-Of-Interests}
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{diagrams/png/conflict-of-interests.png}
\caption{Live+Gov Conflicts of Interests}
\label{figure:Live+Gov Conflicts of Interests}
\end{figure}
%TODO: Adapt Figure

@@

%input{./figures/LG-Vulnerabilities}
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{diagrams/png/vulnerabilities.png}

%\begin{flushleft}
%\scriptsize
%\textbf{Legend:}
%
%\begin{itemize}
%\itemsep1pt\parskip0pt\parsep0pt
%\item
%  \textbf{(a) Citizen:} User of the L+G client application whose privacy
%  is at stake.
%\item
%  \textbf{(b) Mobile Device:} Runs the L+G client application, produces
%  and stores data sensitive to the users privacy.
%\item
%  \textbf{(c) L+G Data Center:} Runs the L+G services, proccesses and
%  stores user data.
%\item
%  \textbf{(d) L+G Maintenance Crew:} Technical staff with access to
%  critical infrastructure.
%\item
%  \textbf{(e) Aggregation Monitor:} Interface to aggregated user data.
%\item
%  \textbf{(f) Local Authority:} Provider of the L+G system.
%\item
%  \textbf{(g) Criminal:} Threatens the L+G system and Citizen privacy.
%\end{itemize}
%\end{flushleft}

\caption{Live+Gov Vulnerabilities}
\label{figure:Live+Gov Vulnerabilities}
\end{figure}

@@

%input{./figures/Threat-Example}
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{diagrams/png/threat-example.png}
\caption{Threat Example}
\label{figure:Threat-Example}
\end{figure}

@@

% \label{figure:Threats}
%input{./figures/Threats}
\begin{figure}
\centering
%\includegraphics[width=\textwidth]{diagrams/png/threat-table.png}
\newcommand{\tcell}[1]{\parbox[c]{6cm}{#1\vspace{3mm}}}
\newcommand{\thead}[1]{\tcell{\vspace{3mm}\centering\textbf{#1}}}
\newcommand{\tbody}[1]{\tcell{\footnotesize\flushleft #1}}
\resizebox{\textwidth}{!}{
\begin{tabular}{|c|c|c|c|}

\hline
\thead{Threat}
& \thead{Conflict of Interest}
& \thead{Vulnerability}
& \thead{Affected Data}
\\\hline\hline
\tbody{Insufficient Control Features}
& \tbody{Privacy vs. System Complexity}
& \tbody{Missing Privacy Awareness}
& \tbody{All collected data}
\\\hline

\tbody{Exessive Data Mining}
& \tbody{Privacy vs. Business Intelligence (LA),
\\Privacy vs. Financial Profit (SP)}
& \tbody{Lax data handling policies
\\Missing Privacy Awareness
\\Weak law enforcement}
& \tbody{Mined Information}
\\\hline

\tbody{Data Theft}
& \tbody{Privacy vs. Financial Profit
\\Reputation (SP) vs. Political Activism
\\Reputation (LA) vs. Political Activism}
& \tbody{Insecure Infrastructure,
\\Insecure Communication}
& \tbody{Transmitted data 
\\Data stored in data center}
\\\hline

\tbody{Surveillance}
& \tbody{Privacy vs. External Power}
& \tbody{Insecure Infrastructure
\\Insecure Communication}
& \tbody{Transmitted data 
\\Data stored in data center}
\\\hline

\tbody{Information Leak}
& \tbody{Privacy vs. Financial Profit
\\Reputation (SP) vs. Political Activism
\\Reputation (LA) vs. Political Activism}
& \tbody{Unhappy Employee 
\\Lax Access Rules}
& \tbody{Data stored in data center}
\\\hline

\tbody{Social Engineering}
& \tbody{Privacy vs. Financial Profit
\\Reputation (SP) vs. Political Activism
\\Reputation (LA) vs. Political Activism}
& \tbody{Unhappy Employee
\\Lax Access Rules}
& \tbody{Data stored in data center}
\\\hline
\end{tabular}
}
\caption{Threats}
\label{figure:Threats}
\end{figure}
